Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-06-07 paper/AlignedIsotropicGW.tex
Rename style file so arXiv doesn't try to use its own nature.cls which has no figures.
Moved plots file for arXiv submission.
changed rounding of number in table

\documentclass{nature}

@@

\begin{table}
\begin{centering}
\begin{tabular}{ c |  c  |  c  | c  }
  \hline 
  \hline
Events & $\sigma_{I/A}$ &  $\sigma_{I/A}$ & $\sigma_{I/A}$ \\ 
 & ``Low'' & ``Flat'' & ``High'' \\ \hline
GW150914 and GW151226 &  1.3 & 2.2 & 3.7 \\ %\hline
All O1 events & 1.7 & 2.7 & 4.4 \\ %\hline
All O1 events and GW170104 & \textbf{2.4} & 3.6 & 5.4 \\ \hline
\end{tabular}
\caption[]{Significance $\sigma_{I/A}$ of the odds ratio between the isotropic and aligned models using just GW150914 and GW151226, all 3 O1 events, and all 4 currently observed events (including GW170104). The number in bold is the result we quote in the main text.}
\label{tab:accumulation}
\end{centering}
\end{table}

@@

\bibliographystyle{naturemag}
\bibliography{AlignedIsotropicGW}

>>>>

\documentclass{nature-arxiv}

@@

\begin{table}
\begin{centering}
\begin{tabular}{ c |  c  |  c  | c  }
  \hline 
  \hline
Events & $\sigma_{I/A}$ &  $\sigma_{I/A}$ & $\sigma_{I/A}$ \\ 
 & ``Low'' & ``Flat'' & ``High'' \\ \hline
GW150914 and GW151226 &  1.3 & 2.2 & 3.7 \\ %\hline
All O1 events & 1.7 & 2.7 & 4.4 \\ %\hline
All O1 events and GW170104 & \textbf{2.4} & 3.5 & 5.4 \\ \hline
\end{tabular}
\caption[]{Significance $\sigma_{I/A}$ of the odds ratio between the isotropic and aligned models using just GW150914 and GW151226, all 3 O1 events, and all 4 currently observed events (including GW170104). The number in bold is the result we quote in the main text.}
\label{tab:accumulation}
\end{centering}
\end{table}

@@

\bibliographystyle{naturemag-arxiv}
\bibliography{AlignedIsotropicGW}
